Risk Perceptions for Wearable Devices

### 2015-01-07 wearables_survey.tex
keywords: wearables -> wearable devices
Overhaul of Discussion: Future Research Directions.

\keywords{Privacy, Security, User Studies, Risk Perception, Ubiquitous Computing, Wearables} % NOT required for Proceedings

@@

\subsection{Future Research Directions}

Our survey shows that photos, videos, and textual information is generally considered to be very sensitive. Various systems which can detect and take actions for sensitive objects in photos and videos will be critical as wearables and other devices become more ubiquitous. We also show that users are significantly more willing to offer certain data if it will only be shared with the application; and additionally, that users consider privacy as their number-one concern. Research in effective sandboxing and other software protections, effective notifications, and usable indicators are encouraged at this time. Lastly, exploratory research investigating user-reported concerns, are relevant--especially the social impact of wearable devices, measurement of inaccuracy of sensor readings presented by wearables, and rate of accidental information sharing.

>>>>

\keywords{Privacy, Security, User Studies, Risk Perception, Ubiquitous Computing, Wearable Devices} % NOT required for Proceedings

@@

\subsection{Future Research Directions}
Wearables are still in their infancy. Perceptions of situations and new capabilities will change rapidly with new capabilities and increased exposure, respectively. However, videos, and textual information is considered to be significantly sensitive by our participants, along with past participants of smartphone user perception studies. Various systems which can detect and take actions for sensitive objects in photos and videos will be critical as wearables and other devices become more ubiquitous.

While privacy and security concerns were expected, consider these unexpected user concerns as starting points for future research: the high financial costs of wearables, health concerns of constant device use, safety issues related to device operation, the social impact of wearable devices, and improving aesthetics of wearables.
